{\small\setlength\baselineskip{10pt}
\begin{thebibliography}{9}
\bibitem{Discord Inc.} Discord - \url{https://discord.com} (accessd on 21 Nov 2023).
\bibitem{noguchi} 野口 悠紀雄, 「超」整理法―情報検索と発想の新システム (中公新書), 中央公論新社, (1993).
\bibitem{Slack Inc.} Slack - \url{https://slack.com/intl/ja-jp/help/articles/115004071768-Slack-%E3%81%A8%E3%81%AF} (accessd on 6 Jan 2024).
\bibitem{agile_development} Agile software development - \url{https://en.wikipedia.org/wiki/Agile\_software\_development} (accessd on 20 Nov 2023).
\bibitem{Ruby_on_Rails} Ruby on Rails - \url{https://rubyonrails.org/} (accessd on 20 Nov 2023).
\bibitem{Matz} まつもとゆきひろ - \url{https://ja.wikipedia.org/wiki/%E3%81%BE%E3%81%A4%E3%82%82%E3%81%A8%E3%82%86%E3%81%8D%E3%81%B2%E3%82%8D} (accessd on 18 Dec 2023).
\bibitem{Qiita} Qiita - \url{https://help.qiita.com/ja/articles/qiita} (accessd on 18 Dec 2023).
\bibitem{RubyGems} RubyGems - \url{https://rubygems.org/} (accessd on 18 Dec 2023).
\bibitem{Heroku} Heroku - \url{https://www.heroku.com/what} (accessd on 18 Dec 2023).
\bibitem{Heroku Add-ons} Heroku Add-ons - \url{https://elements.heroku.com/addons} (accessd on 18 Dec 2023).
\bibitem{CoC} Convention over Configuration - \url{https://en.wikipedia.org/wiki/Convention\_over\_configuration} (accessd on 18 Dec 2023).
\bibitem{Habit man} Habit man - \url{https://membermanagementapp-d0c147b97826.herokuapp.com/}
\bibitem{Heroku Postgres} Heroku Postgres - \url{https://devcenter.heroku.com/ja/articles/heroku-postgresql} (accessd on 29 Jan 2024).
\bibitem{Active Record} Active Recordの基礎 - \url{https://railsguides.jp/active_record_basics.html} (accessd on 29 Jan 2024).
\bibitem{Rails PostgreSQL} Rails コア開発環境の構築方法 - \url{https://railsguides.jp/development_dependencies_install.html} (accessd on 29 Jan 2024).
\bibitem{Heroku Scheduler} Heroku Scheduler - \url{https://devcenter.heroku.com/ja/articles/scheduler} (accessd on 29 Jan 2024).
\bibitem{strong parameters} Strong parameters - \url{https://railsguides.jp/action\_controller\_overview.html\#strong-parameters} (accessd on 3 Dec 2023).
\end{thebibliography}
}
